A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2018-11-29 MS.tex
Changed order of dissection section

Dissection allows the number of completed gonotrophic cycles to be
counted and from this the mean number of cycles before death was
estimated. Overall, the mean number of cycles completed in a lifetime
was 1.3 (posterior mean; Fig. \ref{fig:dissection_lifetimes_exponential}; Table \ref{S-tab:dissection_estimated_lifespans}) and across the 131 studies, 95\% of
the individual time series estimates were less than 3 (Fig. \ref{S-fig:dissection_individualEstimates_allSpecies}). The
estimated greatest number of cycles was for \emph{Anopheles sergentii}
(3.0 cycles; posterior mean) which is adapted to desert conditions (it
is known as the ``oasis vector'' of malaria) and may have evolved
greater longevity. The important African malaria vector \emph{A.
gambiae s.l.} was estimated to be the second longest living (2.4 cycles;
posterior mean). The smallest estimated mean number of gonotrophic
cycles was for \emph{Anopheles} \emph{bellator} (0.6 cycles; posterior
mean) which transmits malaria in Brazil's Atlantic Forest. There were
significant differences in estimated lifetime gonotrophic cycles amongst
species (ANOVA: \emph{F}\textsubscript{24,106} =2.2, \emph{p}
\textless{}0.01; the non-parametric Kruskal Wallace:
\({\chi^{2}}_{24}\), \emph{p}\textless{}0.01).

>>>>

Dissection allows the number of completed gonotrophic cycles to be
counted and from this the mean number of cycles before death was
estimated. Across the 131 studies, 95\% of the individual time series estimates were less than 3 gonotrophic cycles (Fig. \ref{S-fig:dissection_individualEstimates_allSpecies}) and, overall, the mean number of cycles completed in a lifetime
was 1.3 (posterior mean; Fig. \ref{fig:dissection_lifetimes_exponential}; Table \ref{S-tab:dissection_estimated_lifespans}). The
estimated greatest number of cycles was for \emph{Anopheles sergentii}
(3.0 cycles; posterior mean) which is adapted to desert conditions (it
is known as the ``oasis vector'' of malaria) and may have evolved
greater longevity. The important African malaria vector \emph{A.
gambiae s.l.} was estimated to be the second longest living (2.4 cycles;
posterior mean). The smallest estimated mean number of gonotrophic
cycles was for \emph{Anopheles} \emph{bellator} (0.6 cycles; posterior
mean) which transmits malaria in Brazil's Atlantic Forest. There were
significant differences in estimated lifetime gonotrophic cycles amongst
species (ANOVA: \emph{F}\textsubscript{24,106} =2.2, \emph{p}
\textless{}0.01; the non-parametric Kruskal Wallace:
\({\chi^{2}}_{24}\), \emph{p}\textless{}0.01).
